---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spatialbiodiv

<!-- badges: start -->
<!-- badges: end -->

The goal of spatialbiodiv is to calculate spatial and sample-based species
rarefaction curves (sSBR) and distance-decay of similarity curve from
spatially-explicit biodiversity data (i.e.) species presences-absences
or abundances from standardized samples in landscapes.

## Installation

You can install the development version of spatialbiodiv from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FelixMay/spatialbiodiv")
```

## Example

For application examples see "analysis/analyse_sim_dat1.html"

This is a basic example which shows you how to solve a common problem:

```{r example}
library(spatialbiodiv)
## basic example code
```

