---
title: "Test analyses of simulated data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test analyses of simulated data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spatialbiodiv)
library(tidyverse)
library(vegan)
library(scam)
knitr::opts_knit$set(root.dir = "..")
```

# Read and prepare the data

```{r}
getwd()
simdat1 <- read.table("data_raw/GeDo_test5_rep_10_output_sample.txt", header = TRUE,
                      sep = ",")
simdat1 <- simdat1 %>% select(-X)
```

Filter high and low fragmentation scenarios

```{r}
frag_low <- simdat1 %>%
  filter(step == 31 & fragmentation == 0.1)

frag_high <- simdat1 %>%
  filter(step == 31 & fragmentation == 0.5)
```

## Prepare data for spatial biodiversity curves

Get abundance tables with rows in samples and species in columns

```{r}
frag01_spec <- frag_low %>%
  select(sp_1:sp_200)

frag05_spec <- frag_high %>%
  select(sp_1:sp_200)
```

Get spatial coordinates of the samples

```{r}
xy_frag01 <-  frag_low %>%
  select(loc_x, loc_y)

xy_frag05 <-  frag_high %>%
  select(loc_x, loc_y)
```

# Spatial sample-based rarefaction curves (sSBR)

```{r}
sSBR_frag01 <- sSBR(comm = frag01_spec, xy_coords = xy_frag01)
sSBR_frag05 <- sSBR(comm = frag05_spec, xy_coords = xy_frag05)
```

## Create dataframe for plotting with ggplot

```{r}
sSBR_frag01$sSBR_data$fragmentation <- "Low"
sSBR_frag01$sSBR_smooth$fragmentation <- "Low"

sSBR_frag05$sSBR_data$fragmentation <- "High"
sSBR_frag05$sSBR_smooth$fragmentation <- "High"

sSBR_data <- bind_rows(sSBR_frag01$sSBR_data, sSBR_frag05$sSBR_data)
sSBR_smooth <- bind_rows(sSBR_frag01$sSBR_smooth, sSBR_frag05$sSBR_smooth)

```

## Plot the sSBR curves

```{r, fig.height = 5, fig.width = 6}
ggplot(sSBR_data, aes(distance, S, group = interaction(id, fragmentation),
                      color = fragmentation)) +
  geom_line() +
  geom_line(aes(distance, S, color = fragmentation, group = fragmentation),
            data = sSBR_smooth, size = 2) +
  geom_ribbon(aes(x = distance, y = S, ymin = S_low, ymax = S_high,
                  fill = fragmentation, group = fragmentation), color = "black",
              data = sSBR_smooth, alpha = 0.2)
```

# Distance-decay curves

```{r}
dd_frag01 <- dist_decay(comm = frag01_spec, xy_coords = xy_frag01)
dd_frag05 <- dist_decay(comm = frag05_spec, xy_coords = xy_frag05)
```

## Create dataframe for plotting with ggplot

```{r}
dd_frag01$dd_data$fragmentation <- "Low"
dd_frag01$dd_smooth$fragmentation <- "Low"

dd_frag05$dd_data$fragmentation <- "High"
dd_frag05$dd_smooth$fragmentation <- "High"

dd_data <- bind_rows(dd_frag01$dd_data, dd_frag05$dd_data)
dd_smooth <- bind_rows(dd_frag01$dd_smooth, dd_frag05$dd_smooth)
```

## Plot the distance-decay curves

```{r, fig.height = 6, fig.width = 7}
ggplot(dd_data, aes(distance, similarity, color = fragmentation)) +
  geom_point() +
  geom_line(aes(distance, similarity, color = fragmentation, group = fragmentation),
            data = dd_smooth, size = 2)
```
